---
title: "microbes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
```{r warning=FALSE}
library(microbiome)
library(reshape2)
library(DESeq2)
library(ggplot2)
library(dplyr)
library(phyloseq)
library(doBy)
library(ggsci)
library(ggpubr)
library(plyr)
library(ggpubr)
library(cowplot)
library(vegan)
library(usedist)
library(patchwork)
#library(ggcor)
#library(ggcorrplot)
library(corrplot)

# color
mypal = pal_npg()(4)
```

## Required Functions
```{r}
###### get topn taxa
get_topn_taxa <- function(pydata, taxa_level, topn){
  tb = tax_glom(pydata, taxa_level)
  tb_mt = psmelt(tb)
  #return(tb_mt)
  tb_mt_sm = summaryBy(list("Abundance", taxa_level), data=tb_mt, FUN=c(mean, median)) %>% arrange(desc(Abundance.mean))
  tb_mt_sm$rank = 1:nrow(tb_mt_sm)
  new_name = ""
  for (i in 1:nrow(tb_mt_sm)){
    if (i<=topn){
      new_name[i] = as.character(tb_mt_sm[, 1])[i]
    }else{
      new_name[i]="Other"
    }
  }
  tb_mt_sm$new_name = new_name
  plot_format = merge(tb_mt, tb_mt_sm, by = taxa_level)
  #return result              
  result = list(plot_format = plot_format, rank = tb_mt_sm)
  return(result)
}


###### get combinations
get_comb=function(grp){
  comp=list()
  a=combn(unique(grp), 2)
  for (i in 1:ncol(a)) {comp[i]=list(as.character(a[,i]))}
  comp
}


###### get plist
get_plist <- function(physeq, color, shape="NA"){
  dist = "bray"
  ord_meths = c("CCA", "RDA", "PCoA", "DCA", "MDS", "NMDS")
  if (shape != "NA"){
    plist = llply(as.list(ord_meths), function(i, physeq, dist){
        ordi = ordinate(physeq, method=i, distance=dist)
        plot_ordination(physeq, ordi, "Sample", color = color, shape = shape) + theme_bw() + scale_color_npg() + theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + labs(title = i)
}, physeq, dist)
  }else{
    plist = llply(as.list(ord_meths), function(i, physeq, dist){
        ordi = ordinate(physeq, method=i, distance=dist)
        plot_ordination(physeq, ordi, "Sample", color = color) + theme_bw() + scale_color_npg() + theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + labs(title = i)
}, physeq, dist)
  }
  
  names(plist) <- ord_meths
  return(plist)
}

###### get scatter boxplot
get_scatter_boxplot <- function(ggpt, cl){
  pc1=colnames(ggpt$data)[1]
  pc2=colnames(ggpt$data)[2]
  xbox = axis_canvas(ggpt, axis = "x", coord_flip = TRUE) + 
    geom_boxplot(data = ggpt$data, aes_string(y = pc1, x = cl, color = cl)) + 
    scale_x_discrete() + coord_flip() + scale_color_npg()
  ybox = axis_canvas(ggpt, axis = "y") + 
    geom_boxplot(data = ggpt$data, aes_string(y = pc2, x = cl, color = cl)) +
    scale_x_discrete() + scale_color_npg()
  ## join
  pt = insert_xaxis_grob(ggpt, xbox, grid::unit(1, "in"), position = "top") %>%
       insert_yaxis_grob(ybox, grid::unit(1, "in"), position = "right")
  ggdraw(pt)
}

###### get scatter boxplot pvalue 
get_scatter_boxplot_pvalue <- function(ggdata, grp){
  pc1 = "Axis_1"
  pc2 = "Axis_2"
  fmpc1 = as.formula(paste(pc1, grp, sep=" ~ "))
  fmpc2 = as.formula(paste(pc2, grp, sep=" ~ "))
  pvalue1 = data.frame(compare_means(fmpc1, ggdata, group.by = c("Beta") ))
  pvalue2 = data.frame(compare_means(fmpc2, ggdata, group.by = c("Beta") ))
  rbind(pvalue1, pvalue2)
}

## a test for get_scatter_boxplot
# pp = get_scatter_boxplot(p, "NMDS1", "NMDS2", "New_Treat")
#get_scatter_boxplot_pvalue(time_list_data$B$CCA$data, grp = "New_Treat")


###### Plist_aitchison
get_plist_aitchison <- function(physeq){
  dist = "euclidean"
  ord_meths = c("PCoA")
  plist = llply(as.list(ord_meths), function(i, physeq, dist){
        ordi = ordinate(physeq, method=i, distance=dist)
        plot_ordination(physeq, ordi, "Sample") + theme_bw() + scale_color_npg() + theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + labs(title = i)
}, physeq, dist)
  names(plist) <- ord_meths
  return(plist)
}


###### get grouping plot
get_pc_plot <- function(plist_data, group, type){
  if (type == "NMDS"){
    pt =  ggscatter(plist_data$data, x = "NMDS1", y = "NMDS2",
          color = group, palette = "npg",
          ellipse = TRUE, ellipse.type="confidence",ellipse.level = 0.95,
          mean.point = F, star.plot = TRUE, 
          ggtheme = theme_bw() ) + labs(title = type )
  }else if (type == "PCoA" || type == "MDS"){
    pt = ggscatter(plist_data$data, x = "Axis.1", y = "Axis.2",
          color = group, palette = "npg",
          ellipse = TRUE, ellipse.type="confidence",ellipse.level = 0.95,
          mean.point = F, star.plot = TRUE, 
          ggtheme = theme_bw()) + labs(x = plist_data$labels$x, y = plist_data$labels$y, title = type) 
  }else if (type == "CCA"){
    pt = ggscatter(plist_data$data, x = "CA1", y = "CA2",
          color = group, palette = "npg",
          ellipse = TRUE, ellipse.type="confidence",ellipse.level = 0.95,
          mean.point = F, star.plot = TRUE, 
          ggtheme = theme_bw()) + labs(x = plist_data$labels$x, y = plist_data$labels$y, title = type) 
  }else if (type == "RDA"){
    pt = ggscatter(plist_data$data, x = "PC1", y = "PC2",
          color = group, palette = "npg",
          ellipse = TRUE, ellipse.type="confidence",ellipse.level = 0.95,
          mean.point = F, star.plot = TRUE, 
          ggtheme = theme_bw()) + labs(x = plist_data$labels$x, y = plist_data$labels$y, title = type)
  }else if (type == "DCA"){
    pt = ggscatter(plist_data$data, x = "DCA1", y = "DCA2",
          color = group, palette = "npg",
          ellipse = TRUE, ellipse.type="confidence",ellipse.level = 0.95,
          mean.point = F, star.plot = TRUE, 
          ggtheme = theme_bw()) + labs(x = plist_data$labels$x, y = plist_data$labels$y, title = type)
  }else{
    return("Wrong type")
  }
  return(pt)
}

###### get plist (Need optimize)
get_scatter_plit = function(group, plist) {plist %>%
  llply(function(plist_data){
    get_pc_plot(plist_data, group = group, type = plist_data$labels$title) 
  })
}

get_scatter_boxplot_plist = function(group, plist) {plist %>% 
    llply(function(plist_data){
      get_pc_plot(plist_data, group = group, type = plist_data$labels$title) }) %>% 
    llply(function(ggplot_data){
    get_scatter_boxplot(ggplot_data, cl = group)
  })
}

###### run wilcox.test and summary the mean and median of each group. (Bugs here...!!!!!!! Now it only correctly at OTU level... or given a family level matrix)
get_wilcox_result = function(physeq, label, level){
  CLR_mt = psmelt(physeq)
  fm = as.formula(paste("Abundance ~ ", label, sep = "" ) )
  CLR_mt_wilcox = compare_means(fm, CLR_mt, group.by = level) %>% as.data.frame()
  ## summary the means and median
  mm = summaryBy(list("Abundance", c(label, level)), data = CLR_mt, FUN = c(mean, median))
  mm$label = paste(mm[, 2], mm[, 1])
  CLR_mt_wilcox$label1 = paste(CLR_mt_wilcox[, 1], CLR_mt_wilcox[, 3])
  CLR_mt_wilcox$label2 = paste(CLR_mt_wilcox[, 1], CLR_mt_wilcox[, 4])
  out = merge(CLR_mt_wilcox, mm, by.x = "label1", by.y = "label") %>% merge(mm, by.x = "label2", by.y = "label")
  out = out[, -3]
  colnames(out) = gsub(".x", ".group1", colnames(out))
  colnames(out) = gsub(".y", ".group2", colnames(out))
  return(out)
}

#test = get_wilcox_result(sub_test, "New_Treat_Time")

###### deseq2 group
get_deseq_group <- function(physeq, group, label){
  deseq_out = list()
  cbn <- combn(unique(group), 2)
  for(i in 1:ncol(cbn)){
    compared_names = paste(as.character(cbn[,i][1]), as.character(cbn[,i][2]), sep = "_vs_")
    metadata = data.frame(sample_data(physeq))
    sub_sample = metadata[metadata[label][,1] %in% cbn[,i], ]
    sub_name = rownames(sub_sample)
    sub_physeq = prune_samples(sample_names(physeq) %in% sub_name, physeq) 
    sub_physeq_prune = prune_taxa(taxa_sums(sub_physeq) > 0, sub_physeq) 
    fm = as.formula(paste("~", label, sep = " "))
    ds = phyloseq_to_deseq2(sub_physeq_prune, fm)
    dds = DESeq(ds)
    res = results(dds)
    df = as.data.frame(res)
    df$taxon = rownames(df)
    df = df %>% arrange(log2FoldChange, padj)
    deseq_out[i] = list(df)
    names(deseq_out)[i] = compared_names
  }
  deseq_out
}

###### adonis_group
get_anosim_group <- function(phy_dist, physeq, group, label){
  permanova_out = list()
  cbn <- combn(unique(group), 2)
  for(i in 1:ncol(cbn)){
    compared_names = paste(as.character(cbn[,i][1]), as.character(cbn[,i][2]), sep = "_vs_")
    metadata = data.frame(sample_data(physeq))
    sub_sample = metadata[metadata[label][,1] %in% cbn[,i], ]
    sub_name = rownames(sub_sample)
    sub_dist = dist_subset(phy_dist, sub_name)
    fm = as.formula(paste("sub_dist ~ ", label, sep = "" ) )
    permanova_out[i] = adonis(fm, data = sub_sample)
    names(permanova_out)[i] = compared_names
  }
  permanova_out
}

######
get_prevlence_group <- function(physeq, group, label){
  prevalence_out = data.frame()
  cbn <- as.character(unique(group))
  for(i in 1:length(cbn)){
    metadata = data.frame(sample_data(physeq))
    sub_sample = metadata[metadata[label][,1] %in% cbn[i], ]
    sub_name = rownames(sub_sample)
    sub_physeq = prune_samples(sample_names(physeq) %in% sub_name, physeq) 
    otu_prevalence = prevalence(sub_physeq, detection=0.001) %>% as.data.frame()
    otu_prevalence$group = rep(cbn[i], ncol(otu_prevalence))
    otu_prevalence$OTU = rownames(otu_prevalence)
    prevalence_out = rbind(prevalence_out, otu_prevalence)
  }
  colnames(prevalence_out) = c("Prevalence", "group", "OTU")
  prevalence_out = dcast(prevalence_out, OTU~group, value.var = "Prevalence")
  return(prevalence_out)
}
```

## For metaphlan2 result
less metaphlan2.txt | perl -e 'open AB, ">@ARGV[0]"; open TAX, ">@ARGV[1]"; while(<STDIN>){chomp; @s=split /\t/; $otu="OTU".$n; $n++; $o=(join"\t", @s[1..$#s]); @ts=split/\|/, @s[0]; $tso=(join "\t", @ts) ; if($_=~/^clade_name/){print AB "OTU_id\t$o\n"; print TAX "OTU_id\t$s[0]\tPhylum\tClass\tOrder\tGenus\tSpecies\n"; next}; print AB "$otu\t$o\n"; print TAX "$otu\t$tso\n";}' metaphlan2.abundance metaphlan2.tax

# load data (metaphlan2 and SGB)
mapping, taxonomic file and abundance file
```{r warning=T}
setwd("/userdatanode3/data_jinh/virome_dna_rna/03_dna_host/plot")

###### mapping
raw_mp = read.table("mapping.txt", header=T, sep="\t",row.names = 1)
mp = raw_mp 
mp$Sample = rownames(mp)

###### taxa and abundance table.
meta_ab=read.table("metaphlan2.abundance", header=T, row.names = 1, sep = "\t")
meta_tax=read.table("metaphlan2.tax", header=T, row.names=1, sep = "\t")

# subset data only for week0, week4 and week8.
## Note phyloseq input rawdata format must be matrix, not datafarme...
meta_ab = subset(meta_ab, select = as.character(mp$Sample))
meta_ab = meta_ab[which(rowSums(meta_ab)!=0),] # remove OTU not existied in these samples.
meta_tax = meta_tax[rownames(meta_tax) %in% rownames(meta_ab), ] #remove these OTUs taxon


###### Create a phyloseq input
meta_MP = sample_data(raw_mp)
meta_OTU = otu_table(as.matrix(meta_ab), taxa_are_rows = T)
meta_TAX = tax_table(as.matrix(meta_tax))
meta_physeq = phyloseq(meta_OTU, meta_TAX, meta_MP)

```

# S1 Taxa barplot
```{r}
### pure tax
#family_physeq = subset_taxa(meta_physeq, Family != "F_unclass")

###### Phylum level (Here we only choose top 10 taxa)

meta_family_rank = get_topn_taxa(meta_physeq, "Family", 10)


## Phylum bar plot
Family_bar = ggplot(meta_family_rank$plot_format, aes(Sample, Abundance, fill=new_name))+geom_bar(stat="identity", width=1, position = 'fill')+facet_grid(~From_Adults_or_children, scales="free_x",space="free_x")+theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank())+scale_fill_brewer(palette="Set3")

ggsave(Family_bar, file='S1_family_barplot.pdf', width = 8, height = 3)
```

# S2 beta diversity
```{r}
plist = get_plist(meta_physeq, color="From_Adults_or_children")
scatter_plist = get_scatter_plit("From_Adults_or_children", plist)
scatter_box_plist = get_scatter_boxplot_plist("From_Adults_or_children", plist)
plot_list_comb_out = patchwork::wrap_plots(scatter_box_plist)

ggsave(plot_list_comb_out, file= "S2_beta_diversity.pdf", width = 30, height = 20)
# PC pvalue
pdataframe = ldply(plist, function(y){
    df = y$data
    colnames(df)[c(1,2)] = c("Axis_1", "Axis_2")
    df
    }, .id = "Beta")

scatter_boxplot_pvalue = get_scatter_boxplot_pvalue(pdataframe, grp= "From_Adults_or_children")

# adonis
phy_dist = phyloseq::distance(meta_physeq, method="bray")
anosim_bray = get_anosim_group(phy_dist, meta_physeq, mp$From_Adults_or_children, "From_Adults_or_children")
adonis_out = ldply(anosim_bray, function(x){r = x$R2[1];  p = x$`Pr(>F)`[1]; cbind(r, p)} )

adonis_out$name1 = ldply(strsplit(adonis_out$.id, "_vs_") )[,1] ; adonis_out$name2 = ldply(strsplit(adonis_out$.id, "_vs_") )[,2]

write.table(adonis_out,file =  'adonis_out.txt', sep = '\t', quote = F, row.names = F)

id = ""; r=""; p=""; name=""
input = unique(adonis_out$name1)
for (i in 1:length(input)){
  id[i] = paste(input[i], input[i], sep = "_vs_")
  r[i] = 0; p[i] = 1
  name[i] = input[i]
}

r = as.numeric(r); p = as.numeric(p); name = as.character(name)
adonis_out_modif = data.frame(.id = id, r = r, p=p, name1=name, name2=name) %>% rbind(adonis_out)

## change names
name3 = ""; name4 = ""
for (i in 1:nrow(adonis_out_modif)){ 
  nm1 = as.character(adonis_out_modif$name1[i]) ; nm2 = as.character(adonis_out_modif$name2[i])
  if(nm1 > nm2 ){
    name3[i] = nm1 ; name4[i] = nm2
  }else{
    name3[i] = nm2 ; name4[i] = nm1
  }
}

adonis_out_modif$name3 = name3; adonis_out_modif$name4 = name4
adonis_r = arrange(adonis_out_modif, name3, name4) %>% dcast(name3~name4, value.var = "r") 
adonis_p = arrange(adonis_out_modif, name3, name4) %>% dcast(name3~name4, value.var = "p") 

rownames(adonis_r) = adonis_r$name3; rownames(adonis_p) = adonis_p$name3
adonis_r = adonis_r[, -1]; adonis_p = adonis_p[, -1]


#adonis_r[upper.tri(adonis_r)] = t(adonis_r[lower.tri(adonis_r)])
#adonis_p[upper.tri(adonis_p)] = t(adonis_p[lower.tri(adonis_p)])

adonis_plot = corrplot(as.matrix(adonis_r), p.mat = as.matrix(adonis_p), insig = "label_sig",sig.level = c(.0011, .01, .05), pch.cex = 0.8, pch.col = "black",tl.cex=0.8, type = "lower", is.corr = FALSE, diag = F, tl.col = "black")

```

# alpha diversity
```{r}
meta_alpha=estimate_richness(meta_physeq, measures = c("shannon", "simpson", "InvSimpson"))
meta_alpha$Sample=rownames(meta_alpha)
meta_alpha = merge(meta_alpha, mp, by="Sample")
meta_alpha_mt = melt(meta_alpha)
### plot
alpha_plot = ggplot(meta_alpha_mt, aes(y=value, x=From_Adults_or_children,        fill=From_Adults_or_children))+geom_boxplot()+facet_wrap(.~variable, scales = "free") + scale_fill_brewer(palette="Set3")+theme_bw()+ theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank())

## add p-value
compt = get_comb(mp$From_Adults_or_children)

alpha_plot_pvalue = ggplot(meta_alpha_mt, aes(y=value, x=From_Adults_or_children,        fill=From_Adults_or_children))+geom_boxplot()+facet_wrap(.~variable, scales = "free")  +scale_fill_brewer(palette="Set3")+theme_bw()+ theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank()) + stat_compare_means(comparisons = compt)

ggsave(alpha_plot, file="S3_aphla.pdf", width = 10, height = 5)
```

# # procrustes analysis
```{r}
### load RNA_data and DNA_data
dna_bray = phyloseq::distance(meta_physeq, "bray", type="samples")

rnadata = read.table("DNA_virus_abundance.txt", header = T,  sep = "\t")
#rnadata = read.table("RNA_Species_abundance.txt", header = T,  sep = "\t")
rna_bray = vegdist(t(rnadata[, 2:ncol(rnadata)]), method = "bray")

## NMDS
INA = monoMDS(dna_bray)$point %>% as.data.frame()
INB = monoMDS(rna_bray)$point %>% as.data.frame()

rownames(INA) = gsub("D", "", rownames(INA))
rownames(INB) = gsub("D", "", rownames(INB))

INA = INA[order(rownames(INA)), ] ; 
INB = INB[order(rownames(INB)), ] ; 
## procrustes vegan
procrustes.results <- ade4::procuste(INA, INB)

A = procrustes.results$tabX %>% as.data.frame() ; A$Sample = rownames(A)
B = procrustes.results$tabY %>% as.data.frame() ; B$Sample = rownames(B)
INA_sp = INA;  INA_sp$Sample = rownames(INA)
INB_sp = INB;  INB_sp$Sample = rownames(INB)

plot_pro = rbind( A, B)
plot_pro$method = rep(c("Microbes", "DNA"), each = 60)

new_mp = mp; new_mp$Sample = gsub("D", "", new_mp$Sample)
plot_pro = merge(plot_pro, new_mp, by = "Sample")


##### p value 
pro_test = protest(X = INA, Y = INB, scores = "sites", permutations = 999)
# ade4$procuste.rtest(INA, INB, permutations = 999) # Note Observation in ade4 was equal to procuste corr

##### plot 
plot_pro_ggpt = ggplot(plot_pro, aes(MDS1, MDS2, color = From_Adults_or_children, shape = method)) + 
  geom_point(size = 3) +
  geom_line(aes(group = Sample, color = From_Adults_or_children), alpha=0.5) + 
  ggtitle("Procruste rotation comparing MDS from two different viromes\nProcustes correlation = 0.50, p=0.001") + scale_color_npg() + theme_bw()+ theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank())

ggsave(plot_pro_ggpt, file = "procuste_microbes_dna.pdf", width = 7, height = 5, useDingbats = F)

```

# S5 effect size
```{r}
dnadata = read.table("DNA_virus_abundance.txt", header = T,  sep = "\t", row.names = 1) 
rnadata = read.table("RNA_Species_abundance.txt", header = T,  sep = "\t", row.names = 1)
microbe = read.table("metaphlan2.abundance", header = T, row.names = 1,sep = "\t") %>% t()

colnames(dnadata) = gsub("D","", colnames(dnadata))
colnames(rnadata) = gsub("R","", colnames(rnadata))

dnadata = dnadata[rowSums(dnadata)>0, ]

get_effect_size = function(Microbe_Data, Other_Data){
  require(dplyr)
  microbe_name_order = data.frame(names=row.names(microbe), rank=1:nrow(microbe)) ## Get order
  out = list()
  for (i in 1:nrow(Other_Data)){
      OTU_data = data.frame(names=colnames(Other_Data), value=as.numeric(Other_Data[i,]))
      microbe_name_order_mg = merge(microbe_name_order, OTU_data, by = "names") %>% arrange(rank)
      #print(microbe_name_order_mg)
      a = adonis(microbe~microbe_name_order_mg[,3])
      ar = a$aov.tab$R2[1]
      ap = a$aov.tab$`Pr(>F)`[1]
      otu_name = rownames(Other_Data)[i]
      out[otu_name] = list(c(ar, ap))
  }
  out
}

rna_adonis = get_effect_size(microbe, rnadata) %>% ldply()
dna_adonis = get_effect_size(microbe, dnadata) %>% ldply()
write.table(dna_adonis, file="S5_dna_adonis.txt", sep = "\t", row.names = F, quote=F)

## adonis all
# load "fdrtool" library and p-values
library("fdrtool")

dnadata_order = microbe_name_order_mg = merge(microbe_name_order, t(dnadata), by.x = "names", by.y='row.names') %>% arrange(rank)

## extract the vOTUs with qvalue > 0.1
rna_adonis$qvalue = fdrtool(rna_adonis$V2, statistic="pvalue")$qval
dna_adonis$qvalue = fdrtool(dna_adonis$V2, statistic="pvalue")$qval

sig_rna_vout = subset(rna_adonis, qvalue < 0.1) %>% arrange(-V1)  # 25 
sig_dna_vout = subset(dna_adonis, qvalue < 0.1) %>% arrange(-V1) # 3818

sig_rna_data = rnadata[row.names(rnadata) %in% sig_rna_vout$.id, ]
sig_dna_data = dnadata[row.names(dnadata) %in% sig_dna_vout$.id, ]


################# Get rid of the correlation > 0.5
sig_rna_data_corr = psych::corr.test(t(sig_rna_data))$r %>% melt()
sig_rna_data_corr$subject = paste(sig_rna_data_corr$Var1, sig_rna_data_corr$Var2, sep = "")

sig_dna_data_corr = WGCNA::cor(t(sig_dna_data), nThreads=60) %>% melt()
sig_dna_data_corr$subject = paste(sig_dna_data_corr$Var1, sig_dna_data_corr$Var2, sep = "")

corr_sig <- function(sig_vout, sig_data_corr){
  corr_out = list()
  sig_vout[,1] = as.character(sig_vout[,1]); sig_vout[,2] = as.character(sig_vout[,2])
  set='' ; set[1] = sig_vout[1,1]
  for (i in 2:nrow(sig_vout)){
    for (j in 1:length(set)){
      query = paste(sig_vout[i,1], set[j], sep = "")
      sig_data_corr$subject = paste(sig_data_corr[,1], sig_data_corr[,2], sep="")
      corr_coef = subset(sig_data_corr, subject == query)$value
      #print(query)
      swich = 'on'
      if (corr_coef  >0.5){
        corr_info = c(set[j], sig_vout[i,1], which(sig_vout[,1] == set[j]) , i, corr_coef)
        print(paste(corr_info, collapse = ' '))
        corr_out[length(corr_out)+1] = list(corr_info)
        swich = 'off'
        break
      }
    }
    if (swich == 'on'){
      set[length(set)+1] = sig_vout[i,1]
    }
  }
  return(list(cor_filt = set, filt_info = corr_out))
}


rna_cor_filt = corr_sig(sig_rna_vout, sig_rna_data_corr)
dna_cor_filt = corr_sig(sig_dna_vout, sig_dna_data_corr)

dna_rna_corr_c = dna_rna_corr$cor %>% melt()
dna_rna_corr_c = subset(dna_rna_corr_c, value > 0.8 | value < -0.8)
write.table(dna_rna_corr_c, file = 'dna_rna_corr_c.txt', sep = "\t", quote = F, row.names = F)
### order the data 
# Get order of microbes 
microbe_name_order = data.frame(names=row.names(microbe), rank=1:nrow(microbe))

#~ For rna data
sig_rna_data_t = t(sig_rna_data) %>% as.data.frame()
rnadata_arg =  subset(sig_rna_data_t, select = rna_cor_filt$cor_filt)
rnadata_arg_rk = merge(microbe_name_order, rnadata_arg, by.x='names', by.y='row.names') %>% arrange(rank)
rownames(rnadata_arg_rk) = rnadata_arg_rk$names
rnadata_arg_rk =rnadata_arg_rk[, 3:ncol(rnadata_arg_rk)] 

#~ For dna data
sig_dna_data_t = t(sig_dna_data) %>% as.data.frame()
dnadata_arg =  subset(sig_dna_data_t, select = dna_cor_filt$cor_filt)

dnadata_arg_rk = merge(microbe_name_order, dnadata_arg, by.x='names', by.y='row.names') %>% arrange(rank)
dnadata_arg_rk = dnadata_arg_rk[, 3:ncol(dnadata_arg_rk)]

#  combine data (microbe and rna virus)
rna_comb_sig = adonis(microbe~. , data = rnadata_arg_rk )
dna_comb_sig = adonis(microbe~. , data = dnadata_arg_rk )

# RsquareAdj
RNA_R = RsquareAdj(1-rna_comb_sig$aov.tab$R2[length(rna_comb_sig$aov.tab$R2)-1], 60, length(rna_comb_sig$aov.tab$R2)-2)
DNA_R = RsquareAdj(1-dna_comb_sig$aov.tab$R2[length(dna_comb_sig$aov.tab$R2)-1], 60, length(dna_comb_sig$aov.tab$R2)-2)

## Nation adonis
metadata <- as(sample_data(meta_physeq), "data.frame")
meta_physeq_dist = phyloseq::distance(meta_physeq, method="bray")
Nation = adonis(meta_physeq_dist ~ From, data = metadata)
age = adonis(meta_physeq_dist ~ Adults_or_children , data = metadata)
combine = adonis(meta_physeq_dist ~ From_Adults_or_children , data = metadata)
```
## Function for effect size
```{r}
get_effect_size = function(Microbe_Data, Other_Data){
  require(dplyr)
  microbe_name_order = data.frame(names=row.names(Microbe_Data), rank=1:nrow(Microbe_Data)) ## Get order
  out = list()
  for (i in 1:nrow(Other_Data)){
      OTU_data = data.frame(names=colnames(Other_Data), value=as.numeric(Other_Data[i,]))
      microbe_name_order_mg = merge(microbe_name_order, OTU_data, by = "names") %>% arrange(rank)
      #print(microbe_name_order_mg)
      a = adonis(Microbe_Data~microbe_name_order_mg[,3])
      ar = a$aov.tab$R2[1]
      ap = a$aov.tab$`Pr(>F)`[1]
      otu_name = rownames(Other_Data)[i]
      out[otu_name] = list(c(ar, ap))
  }
  out
}

corr_sig <- function(sig_vout, sig_data_corr){
  corr_out = list()
  sig_vout[,1] = as.character(sig_vout[,1]); sig_vout[,2] = as.character(sig_vout[,2])
  set='' ; set[1] = sig_vout[1,1]
  for (i in 2:nrow(sig_vout)){
    for (j in 1:length(set)){
      query = paste(sig_vout[i,1], set[j], sep = "")
      sig_data_corr$subject = paste(sig_data_corr[,1], sig_data_corr[,2], sep="")
      corr_coef = subset(sig_data_corr, subject == query)$value
      #print(query)
      swich = 'on'
      if (corr_coef  >0.5){
        corr_info = c(set[j], sig_vout[i,1], which(sig_vout[,1] == set[j]) , i, corr_coef)
        print(paste(corr_info, collapse = ' '))
        corr_out[length(corr_out)+1] = list(corr_info)
        swich = 'off'
        break
      }
    }
    if (swich == 'on'){
      set[length(set)+1] = sig_vout[i,1]
    }
  }
  return(list(cor_filt = set, filt_info = corr_out))
}



# calculate effect size b to a  (a is main body, b is intervention factors)
effect_size_analysis <- function(a, b){
  require(fdrtool, vegan, plyr, reshape2)
  require(dplyr)
  a = t(a) %>% as.data.frame()
  ## step1 calculate effect size for each item of b.
  adonis = get_effect_size(a, b) %>% ldply()
  adonis$qvalue = fdrtool(adonis$V2, statistic="pvalue")$qval
  sig_vout = subset(adonis, qvalue < 0.1) %>% arrange(-V1)  # qvalue < 0.01
  sig_data = b[row.names(b) %in% sig_vout$.id, ] # subsample the sig data
  #return(sig_data)
  sig_data_corr = WGCNA::cor(t(sig_data), nThreads=12) %>% melt() # Note the number of threads...
  ## step2 rid of the items with strong correlation (Only retain the one with higher effect size). 
  #return(list(votu = sig_vout, corr = sig_data_corr))
  cor_filt = corr_sig(sig_vout, sig_data_corr)
  ## Order the data
  # get the order of a
  ordered_a = data.frame(names=row.names(a), rank=1:nrow(a)) 
  # order the b
  sig_data_cor_filt = t(sig_data) %>% as.data.frame() %>% subset(select = cor_filt$cor_filt)
  combined_ordered_data = merge(ordered_a, sig_data_cor_filt, by.x='names', by.y='row.names') %>% arrange(rank)
  rownames(combined_ordered_data) = combined_ordered_data$names
  combined_ordered_data =combined_ordered_data[, 3:ncol(combined_ordered_data)] 
  ## step3  calculate effect size for combined data
  comb_sig = adonis(a~. , data = rnadata_arg_rk )
  ## step4 calculate effect RsquareAdj for combined data
  adjr = RsquareAdj(1-comb_sig$aov.tab$R2[length(comb_sig$aov.tab$R2)-1], 60, length(comb_sig$aov.tab$R2)-2)
  
  result = list(adjr = adjr, sig_vout = sig_vout)
  return(result)
}


## mic to dna
microbe_v2 = read.table("metaphlan2.abundance", header = T, row.names = 1,sep = "\t")
mic_to_rna = effect_size_analysis(rnadata, microbe_v2)
mic_to_dna = effect_size_analysis(dnadata, microbe_v2)


### plot 
rna_tax = read.table('./RNA_virus.tax ', header = T,sep = "\t")
sig_rna_vout_plot = sig_rna_vout %>% merge(rna_tax, by.x = '.id', by.y='ID') %>% arrange(-V1) %>% head(20)
sig_rna_vout_plot$nm = paste(sig_rna_vout_plot$.id, sig_rna_vout_plot$species, sep = '__')
rna2microbe = ggplot(sig_rna_vout_plot, aes(x=reorder(nm, V1), y=V1))  + geom_bar(stat="identity") + coord_flip()


dna_tax = read.table('./Virus_family.out', header = T,sep = "\t")
sig_dna_vout_plot = sig_dna_vout %>% merge(dna_tax, by.x = '.id', by.y='Scaffold') %>% subset(Family != 'F_unclass') %>% arrange(-V1) %>% head(20)
sig_dna_vout_plot$nm = paste(sig_dna_vout_plot$.id, sig_dna_vout_plot$Family, sep = '__')
dna2microbe = ggplot(sig_dna_vout_plot, aes(x=reorder(nm, V1), y=V1))  + geom_bar(stat="identity") + coord_flip()

ggsave(rna2microbe, file = 'rna2microbe.pdf', width = 6, height = 5)
ggsave(dna2microbe, file = 'dna2microbe.pdf', width = 6, height = 5)
```



## corr
```{r}
library(vegan)
library(SpiecEasi)

dnadata = read.table("DNA_virus_abundance.txt", header = T,  sep = "\t", row.names = 1) 
rnadata = read.table("RNA_Species_abundance.txt", header = T,  sep = "\t", row.names = 1)
micdata = read.table("metaphlan2.abundance", header = T, row.names = 1,sep = "\t")
dna_tax = read.table('./Virus_family.out_v2', header = T,sep = "\t")

colnames(dnadata) = gsub("D","", colnames(dnadata))
colnames(rnadata) = gsub("R","", colnames(rnadata))
dnadata = dnadata[rowSums(dnadata)>0, ]

dna_table = otu_table(dnadata, taxa_are_rows = T)

## order the data
rnadata = rnadata[, order(colnames(rnadata))]
dnadata = dnadata[, order(colnames(dnadata))]
micdata = micdata[, order(colnames(micdata))]

dnadata_filt = dnadata[apply(dnadata, 1,  function(x)(sum(x != 0))>3), ]
##
rna_table = otu_table(rnadata, taxa_are_rows = T)
dna_table = otu_table(dnadata_filt, taxa_are_rows = T)
micro_table = otu_table(micdata, taxa_are_rows = T)


#dna_rna_corr = WGCNA::cor(t(combine), nThreads=60) %>% melt()
name_dna = otu_table(dna_table) %>% as.data.frame()
name_dna = row.names(name_dna)
name_rna = otu_table(rna_table) %>% as.data.frame()
name_rna = row.names(name_rna)

se.mb_dna_rna <- spiec.easi(list(dna_table, rna_table), method='mb', nlambda=100,
              lambda.min.ratio=1e-3, pulsar.params = list(ncores=80))

spiec.graph=adj2igraph(getRefit(se.mb_dna_rna), vertex.attr=list(name=c(name_dna, name_rna)))

library(igraph)
write.graph(spiec.graph,file="spieceasi.ncol.txt",format="ncol")


data(hmp2)
se.hmp2 <- spiec.easi(list(hmp216S, hmp2prot), method='mb', nlambda=40,
              lambda.min.ratio=1e-2, pulsar.params = list(thresh = 0.05, ncores=80))
spiec.graph_test=adj2igraph(getRefit(se.hmp2))


dna_tax_filt_uncalss = subset(dna_tax, Family != 'F_unclass') 
dnadata_filt = dnadata[row.names(dnadata) %in% dna_tax_filt_uncalss$Scaffold,] 
dnadata_filt = dnadata_filt[apply(dnadata_filt, 1,  function(x)(sum(x != 0))>3), ]


rnadata = rnadata[, order(colnames(rnadata))] %>% t()
dnadata_filt = dnadata_filt[, order(colnames(dnadata_filt))] %>% t()
# dna_rna_corr = psych::corr.test(rnadata, dnadata_filt)
library(WGCNA)
dna_rna_corr = corAndPvalue(rnadata, dnadata_filt)
dna_rna_corr_c = dna_rna_corr$cor %>% melt()
dna_rna_corr_p = dna_rna_corr$p %>% melt()


```


## child adults 
```{r}
###### Aitchison distance
## ~ For PA
mmp =  sample_data(raw_mp3) %>% as.data.frame()
phy_dist_aitc_data_N1 = dist_groups(phy_dist_aitc, mmp$N1 )
phy_dist_aitc_data_N2 = dist_groups(phy_dist_aitc, mmp$N2 )
subgroup = c('Within Chinese_adult', 'Within Chinese_children', 'Within Pakistani_adult', 'Within Pakistani_children', 'Between Chinese_children and Pakistani_adults', 'Between Chinese_adults and Chinese_children', 'Between Pakistani_adults and Pakistani_children', 'Between Chinese_adults and Pakistani_children')

subgroup = c('Within Chinese_adult', 'Within Chinese_children', 'Within Pakistani_adult', 'Within Pakistani_children', 'Between Chinese_children and Pakistani_adults', 'Between Chinese_adults and Chinese_children', 'Between Pakistani_adults and Pakistani_children', 'Between Chinese_adults and Pakistani_children')

#phy_dist_aitc_data_sub = subset(phy_dist_aitc_data_N1, Label %in% subgroup)
aitc_data_N1 = ggplot(data = phy_dist_aitc_data_N1, aes(x=Label, y=Distance)) + geom_boxplot() + coord_flip()
aitc_data_N2 = ggplot(data = phy_dist_aitc_data_N2, aes(x=Label, y=Distance)) + geom_boxplot() + coord_flip()

## combine_N1+ N2
combine_data = rbind(phy_dist_aitc_data_N1, phy_dist_aitc_data_N2)
subgroup = c('Within Chinese_adult', 'Within Chinese_children', 'Within Pakistani_adult', 'Within Pakistani_children', 'Between China_all and Pakistani_children', 'Between Pakistani_adults and Pakistani_children', 'Between Chinese_children and Pakistani_all', 'Between Chinese_adults and Chinese_children')

DNA_ca_dist_plot = ggplot(data = subset(combine_data, Label %in% subgroup), aes(x=reorder(Label, Distance, median), y=Distance)) + geom_boxplot() + coord_flip() + theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank())

DNA_ca_dist = compare_means(Distance~Label, subset(combine_data, Label %in% subgroup)) %>% as.data.frame()

ggsave(DNA_ca_dist_plot, file = 'DNA_ca_dist_plot.pdf', width = 5, height = 3)
write.table(DNA_ca_dist, file = 'DNA_ca_dist_pvalue.txt', sep = '\t', row.names = F, quote= F)
```

### children adults 
```{r}
###### Aitchison distance
## ~ For PA
mmp =  sample_data(raw_mp3) %>% as.data.frame()
phy_dist_aitc_data_N1 = dist_groups(phy_dist_aitc, mmp$N1 )
phy_dist_aitc_data_N2 = dist_groups(phy_dist_aitc, mmp$N2 )
subgroup = c('Within Chinese_adult', 'Within Chinese_children', 'Within Pakistani_adult', 'Within Pakistani_children', 'Between Chinese_children and Pakistani_adults', 'Between Chinese_adults and Chinese_children', 'Between Pakistani_adults and Pakistani_children', 'Between Chinese_adults and Pakistani_children')

subgroup = c('Within Chinese_adult', 'Within Chinese_children', 'Within Pakistani_adult', 'Within Pakistani_children', 'Between Chinese_children and Pakistani_adults', 'Between Chinese_adults and Chinese_children', 'Between Pakistani_adults and Pakistani_children', 'Between Chinese_adults and Pakistani_children')

#phy_dist_aitc_data_sub = subset(phy_dist_aitc_data_N1, Label %in% subgroup)
aitc_data_N1 = ggplot(data = phy_dist_aitc_data_N1, aes(x=Label, y=Distance)) + geom_boxplot() + coord_flip()
aitc_data_N2 = ggplot(data = phy_dist_aitc_data_N2, aes(x=Label, y=Distance)) + geom_boxplot() + coord_flip()

## combine_N1+ N2
combine_data = rbind(phy_dist_aitc_data_N1, phy_dist_aitc_data_N2)
subgroup = c('Within Chinese_adult', 'Within Chinese_children', 'Within Pakistani_adult', 'Within Pakistani_children', 'Between China_all and Pakistani_children', 'Between Pakistani_adults and Pakistani_children', 'Between Chinese_children and Pakistani_all', 'Between Chinese_adults and Chinese_children')

DNA_ca_dist_plot = ggplot(data = subset(combine_data, Label %in% subgroup), aes(x=reorder(Label, Distance, median), y=Distance)) + geom_boxplot() + coord_flip() + theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank())

DNA_ca_dist = compare_means(Distance~Label, subset(combine_data, Label %in% subgroup)) %>% as.data.frame()

ggsave(DNA_ca_dist_plot, file = 'DNA_ca_dist_plot.pdf', width = 5, height = 3)
write.table(DNA_ca_dist, file = 'DNA_ca_dist_pvalue.txt', sep = '\t', row.names = F, quote= F)
```

### children adults 
```{r}
raw_mp3 = read.table("./mapping_v3.txt", header=T, sep="\t",row.names = 1)
#row.names(raw_mp3) = gsub('D', '', row.names(raw_mp3))
mp3 = raw_mp3 
mp3$Sample  =rownames(mp3)
meta_MP3 = sample_data(raw_mp3)

meta_physeq3 = phyloseq(meta_OTU, meta_TAX, meta_MP3)
phy_dist = phyloseq::distance(meta_physeq3, method="bray")
meta_physeq_clr = microbiome::transform(meta_physeq3, 'clr')
phy_dist_aitc = phyloseq::distance(meta_physeq_clr, method="euclidean")

# adonis
phy_dist = phyloseq::distance(meta_physeq, method="bray")
mmp =  sample_data(raw_mp3) %>% as.data.frame()


anosim_bray_N1 = get_anosim_group(phy_dist, meta_physeq3, mmp$N1, "N1")
adonis_out_N1 = ldply(anosim_bray_N1, function(x){r = x$R2[1];  p = x$`Pr(>F)`[1]; cbind(r, p)} )
#write.table(adonis_out, file='S2_adonis_out.txt', sep = "\t", row.names = F, quote = F)

anosim_bray_N2 = get_anosim_group(phy_dist, meta_physeq3, mmp$N2, "N2")
adonis_out_N2 = ldply(anosim_bray_N2, function(x){r = x$R2[1];  p = x$`Pr(>F)`[1]; cbind(r, p)} )

combine_adonis_N1_N2 = rbind(adonis_out_N1, adonis_out_N2)
combine_adonis_N1_N2$name1 = ldply(strsplit(combine_adonis_N1_N2$.id, "_vs_") )[,1] ; combine_adonis_N1_N2$name2 = ldply(strsplit(combine_adonis_N1_N2$.id, "_vs_") )[,2]

adonis_barplot = ggplot(combine_adonis_N1_N2, aes(reorder(.id, r), r, fill='black')) + geom_bar(stat="identity", position="dodge") + coord_flip()


## 
phy_dist_aitc_data_N1 = dist_groups(phy_dist_aitc, mmp$N1 )
phy_dist_aitc_data_N2 = dist_groups(phy_dist_aitc, mmp$N2 )
aitc_data_N1 = ggplot(data = phy_dist_aitc_data_N1, aes(x=Label, y=Distance)) + geom_boxplot() + coord_flip()
aitc_data_N2 = ggplot(data = phy_dist_aitc_data_N2, aes(x=Label, y=Distance)) + geom_boxplot() + coord_flip()

## combine_N1+ N2
combine_data = rbind(phy_dist_aitc_data_N1, phy_dist_aitc_data_N2)
subgroup = c('Within Chinese_adult', 'Within Chinese_children', 'Within Pakistani_adult', 'Within Pakistani_children', 'Between China_all and Pakistani_children', 'Between Pakistani_adults and Pakistani_children', 'Between Chinese_children and Pakistani_all', 'Between Chinese_adults and Chinese_children')

mic_ca_dist_plot = ggplot(data = subset(combine_data, Label %in% subgroup), aes(x=reorder(Label, Distance, median), y=Distance)) + geom_boxplot() + coord_flip() + theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank())

mic_ca_dist = compare_means(Distance~Label, subset(combine_data, Label %in% subgroup)) %>% as.data.frame()

ggsave(mic_ca_dist_plot, file = 'mic_ca_dist_plot.pdf', width = 5, height = 3)
write.table(mic_ca_dist, file = 'mic_ca_dist.txt', sep = '\t', row.names = F, quote= F)

anosim_bray_N1 = get_anosim_group(phy_dist, meta_physeq3, mmp$N1, "N1")
adonis_out_N1 = ldply(anosim_bray_N1, function(x){r = x$R2[1];  p = x$`Pr(>F)`[1]; cbind(r, p)} )
#write.table(adonis_out, file='S2_adonis_out.txt', sep = "\t", row.names = F, quote = F)

anosim_bray_N2 = get_anosim_group(phy_dist, meta_physeq3, mmp$N2, "N2")
adonis_out_N2 = ldply(anosim_bray_N2, function(x){r = x$R2[1];  p = x$`Pr(>F)`[1]; cbind(r, p)} )

combine_adonis_N1_N2 = rbind(adonis_out_N1, adonis_out_N2)
combine_adonis_N1_N2$name1 = ldply(strsplit(combine_adonis_N1_N2$.id, "_vs_") )[,1] ; combine_adonis_N1_N2$name2 = ldply(strsplit(combine_adonis_N1_N2$.id, "_vs_") )[,2]

adonis_barplot = ggplot(combine_adonis_N1_N2, aes(reorder(.id, r), r, fill='black')) + geom_bar(stat="identity", position="dodge") + coord_flip()

mic_adonis = mic_ca_dist_plot + adonis_barplot
  ggsave(mic_adonis, file = 'mic_adonis.pdf', width = 10, height = 5)
```

# corr dna rna at family
```{r}
## load dna and rna data
dna_family = read.table('dna_family_matrix', header = T, sep = '\t', row.names = 1)
rna_family = read.table('rna_family_matrix', header = T, sep = '\t', row.names = 1)


heat_map = quickcor(dna_family, rna_family, cor.test = TRUE, ) + geom_circle2() +  scale_fill_viridis_c() + geom_mark(r = NA,sig.thres = 0.05, size = 3, colour = "black")

abc <- corr.test(dna_family, rna_family,method="spearman",adjust="none")
data <- abc$r
p <- abc$p

h2 = heatmap.2(as.matrix(data),col = colorRampPalette(c("navy", "white", "firebrick3"))(50),breaks=seq(-1,1,length=51),scale='none',trace="none",
          key=TRUE,symkey=FALSE,key.title=NA, key.xlab="Spearman’s rho",#keysize=0.06,
          density.info="none", cellnote=note, notecol='black',notecex=0.5, #色块标记设置及标记的颜色和大小
          #colsep=c(0:ncol(data)),rowsep=c(0:nrow(data)),sepcolor="black",sepwidth=c(0.01, 0.01)
)

library(ggplotify)

pp = abc$p %>% melt(); pp$name = paste(pp$Var1, pp$Var2, sep = '_')
rr = abc$r %>% melt(); rr$name = paste(rr$Var1, rr$Var2, sep = '_')

p_r = merge(pp, rr , by='name')
p_r$qvalue = p.adjust(p_r$value.x, method = 'BH')
p_r = p_r %>% subset(qvalue < 0.1)
# q < 0,1

sub_name = c(as.character(p_r$Var1.x), as.character(p_r$Var2.x)) %>% unique()

sub_data = data[row.names(data) %in% sub_name,colnames(data) %in% sub_name ]
sub_p = p[row.names(p) %in% sub_name,colnames(p) %in% sub_name ]

note=matrix("",nrow(sub_p),ncol(sub_p))
for(i in 1:nrow(sub_p)){
     for (j in 1:ncol(sub_p)){
         if(!is.na(sub_p[i,j])){
             if(sub_p[i,j] < 0.001) {note[i,j]="***"
             } else if(sub_p[i,j] < 0.01){ note[i,j]="**"
             } else if(sub_p[i,j] < 0.05) {note[i,j]="*"
             } else {note[i,j]=""}}
     }  
 }

heatmap.2(as.matrix(sub_data),col = colorRampPalette(c("navy", "white", "firebrick3"))(50),breaks=seq(-1,1,length=51),scale='none',trace="none",
          key=TRUE,symkey=FALSE,key.title=NA, key.xlab="Spearman’s rho",#keysize=0.06,
          density.info="none", cellnote=note, notecol='black',notecex=0.5, #色块标记设置及标记的颜色和大小
          #colsep=c(0:ncol(sub_data)),rowsep=c(0:nrow(sub_data)),sepcolor="black",sepwidth=c(0.01, 0.01)
)


ggsave(h2, file = 'heat_map.pdf', width = 12, height = 6)
```

```{r}
### load RNA_data and DNA_data
dnadata = read.table("DNA_virus_abundance.txt", header = T,  sep = "\t", row.names = 1)
rnadata = read.table("RNA_Species_abundance.txt", header = T,  sep = "\t", row.names = 1)
colnames(dnadata) = gsub('D', '', colnames(dnadata))
colnames(rnadata) = gsub('R', '', colnames(rnadata))

get_procuste_test = function(a, b){
  a_dist = vegdist(t(a), method = "bray")
  b_dist = vegdist(t(b), method = "bray")
  INA = monoMDS(a_dist)$point %>% as.data.frame()
  INB = monoMDS(b_dist)$point %>% as.data.frame()
  INA = INA[order(rownames(INA)), ] ; 
  INB = INB[order(rownames(INB)), ] ; 
## procrustes vegan
  procrustes.results <- ade4::procuste(INA, INB)
  A = procrustes.results$tabX %>% as.data.frame() ; A$Sample = rownames(A)
  B = procrustes.results$tabY %>% as.data.frame() ; B$Sample = rownames(B)
  pro_test = protest(X = INA, Y = INB, scores = "sites", permutations = 999)
  pro_test
}

## each group
raw_mp = read.table("mapping.txt", header=T, sep="\t",row.names = 1)
CA = subset(raw_mp, From_Adults_or_children = 'Chinese_adults') %>% row.names()
PA = subset(raw_mp, From_Adults_or_children = 'Pakistani_adults') %>% row.names()
CC = subset(raw_mp, From_Adults_or_children = 'Chinese_children') %>% row.names()
PC = subset(raw_mp, From_Adults_or_children = 'Pakistani_children') %>% row.names()

CA_dnadata = subset(dnadata, select=CA); CA_rnadata = subset(rnadata, select=CA)
PA_dnadata = subset(dnadata, select=PA); PA_rnadata = subset(rnadata, select=PA)
CC_dnadata = subset(dnadata, select=CC); CC_rnadata = subset(rnadata, select=CC)
PC_dnadata = subset(dnadata, select=PC); PC_rnadata = subset(rnadata, select=PC)

CA = get_procuste_test(CA_dnadata, CA_rnadata)
PA = get_procuste_test(PA_dnadata, PA_rnadata)
CC = get_procuste_test(CC_dnadata, CC_rnadata)
PC = get_procuste_test(PC_dnadata, PC_rnadata)
```

## effect size
```{r}
#micro_2rna
library(microbiome)
library(dplyr)
library(plyr)
library(reshape2)


## 
get_effect_size = function(Microbe_Data, Other_Data){
  require(dplyr)
  microbe_name_order = data.frame(names=row.names(Microbe_Data), rank=1:nrow(Microbe_Data)) ## Get order
  out = list()
  for (i in 1:nrow(Other_Data)){
    OTU_data = data.frame(names=colnames(Other_Data), value=as.numeric(Other_Data[i,]))
    microbe_name_order_mg = merge(microbe_name_order, OTU_data, by = "names") %>% arrange(rank)
    #print(microbe_name_order_mg)
    a = adonis(Microbe_Data~microbe_name_order_mg[,3])
    ar = a$aov.tab$R2[1]
    ap = a$aov.tab$`Pr(>F)`[1]
    otu_name = rownames(Other_Data)[i]
    out[otu_name] = list(c(ar, ap))
  }
  out
}

corr_sig <- function(sig_vout, sig_data_corr){
  corr_out = list()
  sig_vout[,1] = as.character(sig_vout[,1]); sig_vout[,2] = as.character(sig_vout[,2])
  set='' ; set[1] = sig_vout[1,1]
  for (i in 2:nrow(sig_vout)){
    for (j in 1:length(set)){
      query = paste(sig_vout[i,1], set[j], sep = "")
      sig_data_corr$subject = paste(sig_data_corr[,1], sig_data_corr[,2], sep="")
      corr_coef = subset(sig_data_corr, subject == query)$value
      #print(query)
      swich = 'on'
      if (corr_coef  >0.5){
        corr_info = c(set[j], sig_vout[i,1], which(sig_vout[,1] == set[j]) , i, corr_coef)
        print(paste(corr_info, collapse = ' '))
        corr_out[length(corr_out)+1] = list(corr_info)
        swich = 'off'
        break
      }
    }
    if (swich == 'on'){
      set[length(set)+1] = sig_vout[i,1]
    }
  }
  return(list(cor_filt = set, filt_info = corr_out))
}



# calculate effect size b to a  (a is main body, b is intervention factors)
effect_size_analysis <- function(a, b){
  pacman::p_load(fdrtool, vegan, reshape2, plyr, dplyr)
  a = t(a) %>% as.data.frame()
  ## step1 calculate effect size for each item of b.
  adonis = get_effect_size(a, b) %>% ldply()
  adonis$qvalue = fdrtool(adonis$V2, statistic="pvalue")$qval
  sig_vout = subset(adonis, qvalue < 0.1) %>% arrange(-V1)  # qvalue < 0.01
  sig_data = b[row.names(b) %in% sig_vout$.id, ] # subsample the sig data
  #return(sig_data)
  sig_data_corr = WGCNA::cor(t(sig_data), nThreads=12) %>% melt() # Note the number of threads...
  ## step2 rid of the items with strong correlation (Only retain the one with higher effect size). 
  #return(list(votu = sig_vout, corr = sig_data_corr))
  cor_filt = corr_sig(sig_vout, sig_data_corr)
  ## Order the data
  # get the order of a
  ordered_a = data.frame(names=row.names(a), rank=1:nrow(a)) 
  # order the b
  sig_data_cor_filt = t(sig_data) %>% as.data.frame() %>% subset(select = cor_filt$cor_filt)
  combined_ordered_data = merge(ordered_a, sig_data_cor_filt, by.x='names', by.y='row.names') %>% arrange(rank)
  rownames(combined_ordered_data) = combined_ordered_data$names
  combined_ordered_data =combined_ordered_data[, 3:ncol(combined_ordered_data)] 
  ## step3  calculate effect size for combined data
  comb_sig = adonis(a~. , data = combined_ordered_data )
  ## step4 calculate effect RsquareAdj for combined data
  adjr = RsquareAdj(1-comb_sig$aov.tab$R2[length(comb_sig$aov.tab$R2)-1], 60, length(comb_sig$aov.tab$R2)-2)
  
  result = list(adjr = adjr, sig_vout = sig_vout, cor_filt = cor_filt, combined_ordered_data = combined_ordered_data)
  return(result)
}

##
setwd("/userdatanode3/data_jinh/virome_dna_rna/03_dna_host/plot")
dnadata = read.table("DNA_virus_abundance.txt", header = T,  sep = "\t", row.names = 1) 
rnadata = read.table("RNA_Species_abundance.txt", header = T,  sep = "\t", row.names = 1)
microbe = read.table("metaphlan2.abundance", header = T, row.names = 1,sep = "\t")

#tax
microbe_tax = read.table("metaphlan2.tax", header = T,sep = "\t")
##
colnames(dnadata) = gsub("D","", colnames(dnadata))
colnames(rnadata) = gsub("R","", colnames(rnadata))
dnadata = dnadata[rowSums(dnadata)>0, ]

## 
#mic_to_dna = effect_size_analysis(dnadata, microbe)

#sig_votu_effect_size = mic_to_dna$sig_vout %>% merge(microbe_tax, by.x = '.id', by.y='OTU_id') %>% arrange(-V1) %>% head(20)

#microbe_2rna = ggplot(sig_votu_effect_size, aes(x=reorder(Species, V1), y=V1) ) + geom_bar(stat="identity") + coord_flip()

#ggsave(microbe_2rna, file = 'microbe_2rna.pdf', width = 5, height = 5) 


### nation 
## chinese
mp  = read.table('./mapping.txt', sep = '\t', header = T)
c.name = subset(mp,From == 'China' )[,1] %>% as.character()

c_dna = subset(dnadata, select=c.name)
c_rna = subset(rnadata, select=c.name)
c_mic = subset(microbe, select=c.name)

## rm 0
c_dna = c_dna[rowSums(c_dna)>0, ]
c_rna = c_rna[rowSums(c_rna)>0, ]
c_mic = c_mic[rowSums(c_mic)>0, ]

c_dna2mic = effect_size_analysis(c_mic, c_dna)
c_rna2mic = effect_size_analysis(c_mic, c_rna)
c_mic2dna = effect_size_analysis(c_dna, c_mic)
c_mic2rna = effect_size_analysis(c_rna, c_mic) #没弄

## 
## Pakistani
p.name = subset(mp,From == 'Pakistani' )$Sample %>% as.character()

p_dna = subset(dnadata, select=p.name)
p_rna = subset(rnadata, select=p.name)
p_mic = subset(microbe, select=p.name)

## rm 0
p_dna = p_dna[rowSums(p_dna)>0, ]
p_rna = p_rna[rowSums(p_rna)>0, ]
p_mic = p_mic[rowSums(p_mic)>0, ]

p_dna2mic = effect_size_analysis(p_mic, p_dna)
p_rna2mic = effect_size_analysis(p_mic, p_rna)
p_mic2dna = effect_size_analysis(p_dna, p_mic)
p_mic2rna = effect_size_analysis(p_rna, p_mic)


```